Cleaning the data

### 2017-12-08 Analysis/data_cleaning.Rmd
Data wrangling finished

## Keeping only the studies with data
data <- data_raw[apply(data_raw[, 3:9], 1, function(X) ifelse(all(X == "-"), FALSE, TRUE)), ]

## Removing rogue NA rows
data <- data[-231,]
```

@@

## clustering
clustering <- c("Neares-neighbor test", "Cluster dendrogram analysis", "neigbor joining of the centroids", "Nearest neigbhor clustering", "Hierarchical clustering", "Branching random walks")
tests <- multi.gsub(clustering, "clustering", tests)

@@

## Clean the matchings
tests <- gsub("distance Plinear", "linear", tests)
tests <- gsub("multivariate t_test \\(Hotellings' T\\^2 test\\)", "t_test", tests)
tests <- gsub("anova , LDA", "anova + LDA", tests)
tests <- gsub("Kruskal-Wallis", "anova", tests)

@@

```{r}
phylo <- c("yes", "no", "mapped")

factors <- list("data type" = data_type, "full organism" = full_organism, "morphospace" = morphospace, "disparity" = disparity, "test" = test, "phylo correction" = phylo)
```

>>>>

## Keeping only the studies with data
data <- data_raw[apply(data_raw[, 3:9], 1, function(X) ifelse(all(X == "-"), FALSE, TRUE)), ]
```

@@

## clustering
clustering <- c("Nearest-neighbour test", "Cluster dendrogram analysis", "neighbour joining of the centroids", "Nearest-neighbour clustering", "Hierarchical clustering", "Branching random walks")
tests <- multi.gsub(clustering, "clustering", tests)

@@

## Clean the matchings
tests <- gsub("distance Plinear", "linear", tests)
tests <- gsub("multivariate t_test \\(Hotellings' T\\^2 test\\)", "t_test", tests)
tests <- gsub("Kruskal-Wallis", "anova", tests)

@@

## Phylogeny

```{r}
phylogeny <- data[,9]

phylogeny <- multi.gsub("Yes \\(pPC\\)", "pPC", phylogeny)
phylogeny <- ifelse(phylogeny == "", NA, phylogeny)

phylogeny_categories <- unique(unlist(strsplit(unique(phylogeny), split = " \\+ ")))

data[,9] <- phylogeny
```

## Wrapping up the data set

```{r}
## Cleaned data
data <- data[,-c(1,2)]
cleaned_data <- list("data" = data)
cleaned_data$factors <- list(data_taxa = data_taxa_categories, data_type = data_type_categories, full_organism = full_organism_categories, morphospaces = morphospaces_categories, disparity = disparity_categories, tests = tests_categories, phylogeny = phylogeny_categories)

## Save the file
saveRDS(cleaned_data, file = paste0("../Data/Processed/cleaned_data.Rda"))

```
